\documentclass[]{BasiliskReportMemo}
\usepackage{AVS}


\newcommand{\submiterInstitute}{Autonomous Vehicle Simulation (AVS) Laboratory,\\ University of Colorado}

\newcommand{\ModuleName}{test\textunderscore test$\_$ephemerisconvert.py}
\newcommand{\subject}{Testing Ephemeris Conversion}
\newcommand{\status}{Initial document draft}
\newcommand{\preparer}{T. Teil}
\newcommand{\summary}{This unit test the ephemeris conversion module by comparing the messages before and after the module has acted on them, and assuring that the desired results are obtained}


\begin{document}


\makeCover
%
%	enter the revision documentation here
%	to add more lines, copy the table entry and the \hline, and paste after the current entry.
%
\pagestyle{empty}
{\renewcommand{\arraystretch}{1.1}
\noindent
\begin{longtable}{|p{0.5in}|p{4.5in}|p{1.14in}|}
\hline
{\bfseries Rev}: & {\bfseries Change Description} & {\bfseries By} \\
\hline
Draft & Initial document creation & T. Teil \\
\hline

\end{longtable}
}

\newpage
\setcounter{page}{1}
\pagestyle{fancy}

\tableofcontents
~\\ \hrule ~\\



\section{Introduction}
This test set's up an appropriate simulation by creating a Spice Object, which will write messages containing ephemerides. A ephemeris converter object is also created with the map between the message names. This test guarantees that the data is properly copied.


\section{{\tt test\textunderscore test$\_$ephemerisconvert} Test Description}

This test is located in {\tt SimCode/environment/ephemeris$\_$converter/$\_$UnitTest/test$\_$ephemerisconvert.py}. \par

\section{Test Setup}

The spice object was set on the following date: 2015 February 10, 00:00:00.0 TDB, and the planets that were loaded where the Earth, Mars Barycenter, and the Sun.

\subsubsection*{Successful link test}

A boolean variable is added for logging and is verified to have successfully linked the desired messages.

\subsubsection*{Successful copy test}

For each of the celestial bodies who get a message output, we log the two messages that contain their position and velocities in the inertial frames. For mars the first message is the Spice message is $\texttt{mars$\_$planet$\_$data}$
and the second message is the ephemeris converted data $\texttt{mars$\_$ephemeris$\_$data}$. If the norm of their difference (including the time component of the vector), at any time, is greater than our error tolerance $\epsilon =10^{-10}$, then the test fails.


\section{Test Results}

\subsection{Pass/Fail results}

Both components of the test pass. The copy is therefore a properly executed.





\end{document}
