% !TEX root = ./Basilisk-atmosphere-20190221.tex

\section{User Guide}

\subsection{General Module Setup}
This section outlines the steps needed to add an Atmosphere module to a sim.
First, the atmosphere must be imported and initialized:
\begin{verbatim}
from Basilisk.simulation import exponentialAtmosphere
newAtmo = exponentialAtmosphere.ExponentialAtmosphere()
newAtmo.ModelTag = "ExpAtmo"
\end{verbatim}
By default the module uses parameters such that there is no neutral density, and the output is zero'd.  To add specific exponential atmosphere model parameters, use:
\begin{verbatim}
    newAtmo.exponentialParams.baseDensity = baseDensityValue
    newAtmo.exponentialParams.scaleHeight = scaleHeightValue
    newAtmo.planetRadius = planetRadiusValue
\end{verbatim}
To specify a preset exponential model, such as for Earth, the following macro can be used:
\begin{verbatim}
	simSetPlanetEnvironment.exponentialAtmosphere(newAtmo, "earth")
\end{verbatim}

The model can then be added to a task like other simModels. Each Atmosphere calculates atmospheric parameters based on the output state messages for a set of spacecraft.

To add spacecraft to this module, use
\begin{verbatim}
newAtmo.addSpacecraftToModel(scObject.scStateOutMsg)
\end{verbatim}
where {\tt sc0InMsg} is the spacecraft state output message.  This command can be run multiple times to add more than 1 spacecraft.  Note that the order of the vector of output messages will match the order that these spacecraft are added.  By adding the spacecraft this routine will subscribe the spacecraft output message as an input message to this module.

\subsection{Planet Ephemeris Information}
The optional planet state message name can be set by directly adjusting that attribute of the class:
\begin{verbatim}
newAtmo.planetPosInMsg.subscribeTo(planetMsg)
\end{verbatim}
If SPICE is not being used, the planet is assumed to reside at the origin.

\subsection{Setting the Model Reach}
By default the model doesn't perform any checks on the altitude to see if the specified atmosphere model should be used.  This is set through the parameters {\tt envMinReach} and {\tt envMaxReach}.  Their default values are -1.  If these are set to positive values, then if the altitude is smaller than {\tt envMinReach} or larger than {\tt envMaxReach}, the density is set to zero.

