% README file for moduleDocumentationTemplate TeX template.
% This template should be used to document all Basilisk modules.
% Updated 20170711 - S. Carnahan
%
%-Copy the contents of this folder to your own _Documentation folder
%
%-Rename the Basilisk-moduleDocumentationTemplate.tex appropriately
%
% All edits should be made in one of:
% sec_modelAssumptionsLimitations.tex
% sec_modelDescription.tex
% sec_modelFunctions.tex
% sec_revisionTable.tex
% sec_testDescription.tex
% sec_testParameters.tex
% sec_testResults.tex
% sec_user_guide.tex
%
%-Some rules about referencing within the document:
%1. If writing the suer guide, assume the module description is present
%2. If writing the validation section, assume the module features section is present
%3. Make no other assumptions about any sections being present. This allow for sections of the document to be used elsewhere without breaking.

%In order to import some of these sections into a document in a different directory:
%\usepackage{import}
%Then, the sections are called with \subimport{relative path}{file} in order to \input{file} using the right relative path.
%\import{full path}{file} can also be used if absolute paths are preferred over relative paths.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\documentclass[]{BasiliskReportMemo}

\usepackage{cite}
\usepackage{AVS}
\usepackage{float} %use [H] to keep tables where you put them
\usepackage{array} %easy control of text in tables
\usepackage{graphicx}
\bibliographystyle{plain}


\newcommand{\submiterInstitute}{Autonomous Vehicle Simulation (AVS) Laboratory,\\ University of Colorado}


\newcommand{\ModuleName}{hingedRigidBodyStateEffector}
\newcommand{\subject}{Hinged Rigid Body Dynamics Model}
\newcommand{\status}{Reviewed}
\newcommand{\preparer}{C. Allard}
\newcommand{\summary}{The hinged rigid body class is an instantiation of the state effector abstract class. The integrated test is validating the interaction between the hinged rigid body module and the rigid body hub that it is attached to. In this case, a hinged rigid body has a diagonal inertia tensor and is attached to the hub by a single degree of freedom torsional hinged with a linear spring constant and linear damping term. The integrated tests has six scenarios it is testing. The first three are: one with gravity and no damping, one without gravity and without damping, and one without gravity with damping. These first three tests are verifying energy and momentum conservation. In the first two cases orbital energy, orbital momentum, rotational energy, and rotational angular momentum should all be conserved. In the third case orbital momentum, orbital energy, and rotational momentum should be conserved. This integrated test validates for all three scenarios that all of these parameters are conserved. The fourth scenario is verifying that the steady state deflection while a constant force is being applied matches the back of the envelope (BOE) calculation. The fifth scenario applies a constant force and removes the force and the test verifies that the frequency and amplitude match the BOE calculations. And the sixth scenario verifies that Basilisk gives identical results to a planar Lagrangian dynamical system created independently.}

\begin{document}

\makeCover

%
%	enter the revision documentation here
%	to add more lines, copy the table entry and the \hline, and paste after the current entry.
%
\pagestyle{empty}
{\renewcommand{\arraystretch}{2}
\noindent
\begin{longtable}{|p{0.5in}|p{3.5in}|p{1.07in}|p{0.9in}|}
\hline
{\bfseries Rev} & {\bfseries Change Description} & {\bfseries By}& {\bfseries Date} \\
\hline
1.0 & Initial Draft & C. Allard & 20170703\\
\hline
1.1 & Format Changes & C. Allard & 20170712\\
\hline
2.0 & 3 Additional Tests Added & C. Allard & 20170728\\
\hline
2.1 & Frequency and mag tests updated & C. Allard & 20170803\\
\hline
\end{longtable}
}



\newpage
\setcounter{page}{1}
\pagestyle{fancy}

\tableofcontents %Autogenerate the table of contents
~\\ \hrule ~\\ %Makes the line under table of contents










	
\input{secModelDescription.tex} %This section includes mathematical models, code description, etc.

\input{secModelFunctions.tex} %This includes a concise list of what the module does. It also includes model assumptions and limitations

\input{secTest.tex} % This includes test description, test parameters, and test results

\input{secUserGuide.tex} % Contains a discussion of how to setup and configure  the BSK module







\bibliography{bibliography} %This includes references used and mentioned.

\end{document}
