\documentclass[]{BasiliskReportMemo}
\usepackage{AVS}


\newcommand{\submiterInstitute}{Autonomous Vehicle Simulation (AVS) Laboratory,\\ University of Colorado}

\newcommand{\ModuleName}{test\textunderscore hingedRigidBodyStateEffector}
\newcommand{\subject}{Integrated test that validates the hinged rigid body state effector}
\newcommand{\status}{Initial document draft}
\newcommand{\preparer}{C. Allard}
\newcommand{\summary}{The hinged rigid body class is an instantiation of the state effector abstract class. This integrated test is validating the interaction between the hinged rigid body module and the rigid body hub that it is attached to. In this case, a hinged rigid body has a diagonal inertia tensor and is attached to the hub by a single degree of freedom torsional hinged with a linear spring constant and linear damping term. The integrated tests has two scenarios it is testing: one with gravity and one without gravity. In both cases orbital energy, orbital momentum, rotational and deformable energy, and rotational angular momentum should all be conserved. This integrated test validates for both scenarios that all these paramters are conserved.}


\begin{document}


\makeCover
%
%	enter the revision documentation here
%	to add more lines, copy the table entry and the \hline, and paste after the current entry.
%
\pagestyle{empty}
{\renewcommand{\arraystretch}{1.1}
\noindent
\begin{longtable}{|p{0.5in}|p{4.5in}|p{1.14in}|}
\hline
{\bfseries Rev}: & {\bfseries Change Description} & {\bfseries By} \\
\hline
Draft & Initial document creation & C. Allard \\
\hline

\end{longtable}
}

\newpage
\setcounter{page}{1}
\pagestyle{fancy}

\tableofcontents
~\\ \hrule ~\\



\section{Module Introduction}
The hinged rigid body class is an instantiation of the state effector abstract class. The state effector abstract class is a base class for modules that have dynamic states or degrees of freedom with respect to the rigid body hub. Examples of these would be reaction wheels, variable speed control moment gyroscopes, fuel slosh particles etc. Since the state effectors are attached to the hub, the state effectors are directly affecting the hub as well as the hub is back affecting the state effectors.

Specifically a hinged rigid body state effector is a rigid body that 

\section{Module Intended Use}

\section{Module Assumptions/Limitations}

\section{Test Description and Success Criteria}

This test is located in \tt SimCode/dynamics/HingedRigidBodies/UnitTest/\newline
test\_hingedRigidBodyStateEffector.py 


\section{Test Parameters}

\section{Test Results}

\input{AutoTex/ChangeInOrbitalAngularMomentumNoGravity}
\input{AutoTex/ChangeInOrbitalEnergyNoGravity}
\input{AutoTex/ChangeInRotationalAngularMomentumNoGravity}
\input{AutoTex/ChangeInRotationalEnergyNoGravity}
\input{AutoTex/VelocityOfCenterOfMassNoGravity}
\input{AutoTex/ChangeInVelocityOfCenterOfMassNoGravity}


\end{document}
